InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-01-17 paper.tex
Sort detectors by modality
Extend the method section with text processors

The \textbf{RoBERTa Base OpenAI Detector} is the output detector model of GPT-2 \cite{solaiman2019release}. It was obtained by fine-tuning a RoBERTa base model with the outputs of the GPT-2 model containing 1,5 Billion parameters. The RoBERTa Base OpenAI Detector can be used to classify texts, on whether they are likely to be created by the GPT-2 model. It was published by OpenAI, when the weights of the GPT-2 model 1,5 Billion parameter version was released. The model is limited to English texts only and is openly available under the MIT license.

@@

We used the aforementioned models for generating and detecting texts and images. As for image processors, one was already given in the description of the "InformatiCup2024" \cite{InformatiCup}, the image noising using the Gaussian noise. Image noise is the random variation of brightness or color information in images produced by the sensor and circuitry of a scanner or digital camera. The reason why the Gaussian one, also called normal noise, is being used, is because it is being caused by natural sources and the most common noise that affects images naturally \cite{mohammed2016study}. \\
There are several types of noise that can affect images. Some of these noise models are: Gaussian noise, White noise, Fractal noise, Salt \& Pepper noise, Periodic noise, Quantization noise, Speckle noise, Poisson noise, Poisson-Gaussian noise, Structured noise, Gamma noise and Rayleigh noise \cite{gonzalez2009digital}. The three common types of image noise are: Gaussian noise, Salt \& Pepper noise, and Speckle noise \cite{al2010comparative}. That is why we used those three, as well as the Poisson noise.

>>>>

The \textbf{RoBERTa Base OpenAI Detector} is the output detector model of GPT-2. It was obtained by fine-tuning a RoBERTa base model with the outputs of the GPT-2 model containing 1,5 Billion parameters. The RoBERTa Base OpenAI Detector can be used to classify texts, on whether they are likely to be created by the GPT-2 model. It was published by OpenAI, when the weights of the GPT-2 model 1,5 Billion parameter version was released.

@@

We used the aforementioned models for generating and detecting texts and images. As for image processors, one was already given in the description of the "InformatiCup2024" \cite{InformatiCup}, the image noising using the Gaussian noise. Image noise is the random variation of brightness or color information in images produced by the sensor and circuitry of a scanner or digital camera. The reason why the Gaussian one, also called normal noise, is being used, is because it is being caused by natural sources and the most common noise that affects images naturally \cite{mohammed2016study}.

There are several types of noise that can affect images. Some of these noise models are: Gaussian noise, White noise, Fractal noise, Salt \& Pepper noise, Periodic noise, Quantization noise, Speckle noise, Poisson noise, Poisson-Gaussian noise, Structured noise, Gamma noise and Rayleigh noise \cite{gonzalez2009digital}. The three common types of image noise are: Gaussian noise, Salt \& Pepper noise, and Speckle noise \cite{al2010comparative}. That is why we used those three, as well as the Poisson noise.

As for text processors, we evaluated on three different methods of augmenting the text. The first approach is to replace every white-space in a given text, by two white-spaces. The second approach is to add some typos to the texts. This has been implemented based on the nlpaug library, which is capable of simulating certain typos as if they were made on a keyboard by a human. The typos include mistakes, like not hitting the right key, but a key close to the one, that should have been hit instead. This results in typos close to real typos by humans. The last approach is a translator, which has been used to translate the given text into a certain language (in this case French) and re-translate it into english. As translator are not deterministic but aim to keep the semantic meaning, the resulting text should be semantically the same, but might have a different formulation.
